---
title: "Feeding and changing summary"
output: html_document
---

```{r setup, warning = F, message = F, echo = F}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lubridate)
library(reactable)
library(plotly)
library(knitr)
library(here)

opts_chunk$set(warning = FALSE, message = FALSE, echo = F)

source(here('R/funcs.R'))

load(file = here('data/dlydat.RData'))
load(file = here('data/wgtdat.RData'))
load(file = here('data/lendat.RData'))

blddt <- Sys.time()
blddt <- with_tz(blddt, tzone = 'EST')
```

The first tab shows results to date for feeding and diaper change logs for JLB, born Feb. 17th, 2022 at 7:25 PM (Eastern Standard Time).  The results are updated automatically every 24 hours. The second tab shows weight and length at age charts up to 36 months. Source data are available [here](https://docs.google.com/spreadsheets/d/1TOIquQt2WtM1FpQjc1uKp1GRdbYxen0zD9g78gYcmV8/edit?usp=sharing) and the source repository is available [here](https://github.com/fawda123/baby-stats).  

Last report build: `r blddt` EST

# {.tabset .tabset-pills}

## Feeding and diaper changes 

### Daily summaries

```{r}
daysum_tab(dlydat)
```

### Totals to date 

```{r}
totsum_tab(dlydat)
```

### Feedings by hour and duration

```{r}
fdsum_plo(dlydat)
```

### Changes by hour

```{r}
chsum_plo(dlydat)
```

## Growth charts

```{r, fig.height = 8, fig.width = 8}
MygrowthFun(sex = "m", type = "wac36", name = "Jack", surname = "Beck", birth_date = "Feb. 17th, 2022", mydataAA = wgtdat)
```

```{r, fig.height = 8, fig.width = 8}
MygrowthFun(sex = "m", type = "lac36", name = "Jack", surname = "Beck", birth_date = "Feb. 17th, 2022", mydataAA = lendat)
```

